Lifting CDCL to Numerical Domains

### 2016-10-10 example.tex
example description

\section{Motivating Example}
%
\begin{figure}[t]
\scriptsize
\begin{tabular}{l|l|l}
\hline
C program & CFG & Solver Statistics\\
\hline
\begin{lstlisting}[mathescape=true,language=C]
void main() {
 int x,result1=0,result2=0;
 assume(x>=1 && x<= N);
 result1 = 2*x; 
 int state = 1;
 int y=x;
 while(state!=0) {
  switch(state) {
   case 0: state = 1; break;
   case 1: state = 2; break;
   case 2: x--; y++;
   if(x == 0) state = 0;
   else state = 1; break;
  } 
 }
 result2 = y;
 assert(result1 == result2);
}
\end{lstlisting}
&
\begin{minipage}{4.40cm}
\centering
\vspace*{0.3cm}
\scalebox{.45}{\import{figures/}{example.pspdftex}}
%\caption{A control flow graph for P, P' and abstract conflict graph (ACFG) \label{fig:filter}}
\end{minipage}
&
\begin{lstlisting}[mathescape=true,language=C]
                 SAT solver  ACDCL  
restarts           1          0
conflicts  :       5          2
decisions  :       36         2 
propagations :     1365       240  
conflict literals  65         2   
\end{lstlisting}
\\
\hline
\end{tabular}
\caption{C Program, and statistics for decision procedure}
\label{example}
\end{figure}

>>>>

\section{Motivating Example}
%
\begin{figure}[t]
\scriptsize
\begin{tabular}{l|l|l}
\hline
C program & Control-Flow Graph & Decision Procedure Statistics\\
\hline
\begin{lstlisting}[mathescape=true,language=C]
void main() {
 int x,result1=0,result2=0;
 assume(x>=1 && x<= N);
 result1 = 2*x; 
 int state = 1;
 int y=x;
 while(state!=0) {
  switch(state) {
   case 0: state = 1; break;
   case 1: state = 2; break;
   case 2: x--; y++;
   if(x == 0) state = 0;
   else state = 1; break;
  } 
 }
 result2 = y;
 assert(result1 == result2);
}
\end{lstlisting}
&
\begin{minipage}{4.40cm}
\centering
\vspace*{0.3cm}
\scalebox{.45}{\import{figures/}{example.pspdftex}}
%\caption{A control flow graph for P, P' and abstract conflict graph (ACFG) \label{fig:filter}}
\end{minipage}
&
\begin{lstlisting}[mathescape=true,language=C]
                 SAT solver  ACDCL 
                 ----------- ----- 
restarts           1          0
conflicts  :       5          2
decisions  :       36         2 
propagations :     1365       240  
conflict literals  65         4   
\end{lstlisting}
\\
\hline
\end{tabular}
\caption{C Program, CFG and statistics for decision procedure}
\label{example}
\end{figure}
Let us consider a simple program in Figure~\ref{example} that checks 
the equivalence of a state-machine based interger multiplication against  
a specification that uses multiplication operator (*).  The assertion 
simply compares the result of two multiplication for an input $x$.  To 
avoid overflow error, we assume $x$ has an upper bound $N$.  The 
control flow graph is shown in the middle column of Figure~\ref{example}.

We analyze the program using three different analyzers -- {\em bounded 
model checking (BMC)}, {\em abstract interpretation} and {\em ACDCL}.    
For $N=2$ and unwind limit of $bound=4$ for the {\em while} loop, the 
right column shows the statistics from MiniSAT~\cite{minisat} solver 
for analysis using BMC.  The SAT solver makes 36 decisions, 1365 boolean 
constraint propagations and performs 5 conflict analysis with 65 conflict 
literals.  Moreover, the solver performs a restart, presumably to recover 
from bad decisions.

On the other hand, abstract interpretation using forward analysis 
is too imprecise to verify the safety of the above program using 
interval domain.  The imprecision is due to control-flow join at 
node $n1$.  State-of-the-art abstract interpretation tool, Astr{\'e}e, 
requires external hints, provided by manually annotating the code 
with partition directives at $n1$, to prove safety.  The partition 
directive helps the tool to analyze each program execution paths separately.  
To do so, Astr{\'e}e requires a trace partitioning domain along with interval 
to determine safety.  Consequently, the analysis becomes very expensive 
for a large value of $N$.  In general, the imprecision is either intended 
  by the tool because such high precision analysis is normally not required for runtime error analysis or the imprecision is unavoidable due to the complexity 
of the application under analysis.

Figure~\ref{} shows an analysis using ACDCL with interval domain.  The 
analysis associates an interval for each control location and variable, 
as shown in the abstract conflict graph.

The result of the analysis is shown in right side of Figure~\ref{example}.  
Compared to a SAT solver, ACDCL makes only a single decisions which lead 
to 240 interval constraint propagations, and learns a single conflict clause 
involving only one literal.
